### 2013-02-03 proposal/pixel_level.tex
rearrangement

>>>>

\paragraph{tests with real data}
We have identified the \project{HAWK-I} camera on \project{Paranal} as
a possible analog.  It appears to have flat-field morphology similar
to that expected for the \project{Euclid} infrared camera, and it is
the same detector technology.  The next steps are
\begin{itemize}
\item Find and download a range of science data taken in one chosen
  filter with a range of exposure times.
\item Choose a small patch of the detector where there is known to be
  good or interesting flat-field structure.
\item Make source and sky patches from those data, and do some
  analysis.
\end{itemize}
